\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-18 paper.qmd
Added interp citation
Added references for hex binning

Although there are several implementations of hexagon binning (REF), and a published paper (REF), surprisingly, none has sufficient detail or components that produce everything needed for this project. So we described the process used here. @fig-hex-param illustrates the notation used.

@@

To ensure that the grid covers the range of data values a buffer parameter ($q$) is set as a proportion of the range. By default,  $q=0.1$. The buffer should be extending a full hexagon width ($a_1$) and height ($a_2$) beyond the data, in all directions. The lower left position where the grid starts is defined as $(s_1, s_2)$, and corresponds to the centroid of the lowest left hexagon, $C_{1}^{(2)} = (c_{11}, c_{12})$. This must be smaller than the minimum data value. Because it is one buffer unit, $q$ below the minimum data values, $s_1 = -q$ and $s_2 = -r_2*q$.

@@

Delaunay triangulation [@lee1980] (XXXREF what R package are you using?) is used to connect neighboring centroids. The edges are needed to preserve neighborhood information when the model is lifted into \pD{}.

>>>>

Although there are several implementations of hexagon binning [@carr1987], and a published paper [@dan2023], surprisingly, none has sufficient detail or components that produce everything needed for this project. So we described the process used here. @fig-hex-param illustrates the notation used.

@@

To ensure that the grid covers the range of data values a buffer parameter ($q$) is set as a proportion of the range. By default,  $q=0.1$. The buffer should be extending a full hexagon width ($a_1$) and height ($a_2$) beyond the data, in all directions. The lower left position where the grid starts is defined as $(s_1, s_2)$, and corresponds to the centroid of the lowest left hexagon, $C_{1}^{(2)} = (c_{11}, c_{12})$. This must be smaller than the minimum data value. Because it is one buffer unit, $q$ below the minimum data values, $s_1 = -q$ and $s_2 = -qr_2$.

@@

Delaunay triangulation [@lee1980;@alb2024] is used to connect neighboring centroids. The edges are needed to preserve neighborhood information when the model is lifted into \pD{}.

### 2024-07-18 paper.tex
Added references for hex binning

Although there are several implementations of hexagon binning (REF), and
a published paper (REF), surprisingly, none has sufficient detail or
components that produce everything needed for this project. So we
described the process used here. Figure~\ref{fig-hex-param} illustrates
the notation used.

@@

To ensure that the grid covers the range of data values a buffer
parameter (\(q\)) is set as a proportion of the range. By default,
\(q=0.1\). The buffer should be extending a full hexagon width (\(a_1\))
and height (\(a_2\)) beyond the data, in all directions. The lower left
position where the grid starts is defined as \((s_1, s_2)\), and
corresponds to the centroid of the lowest left hexagon,
\(C_{1}^{(2)} = (c_{11}, c_{12})\). This must be smaller than the
minimum data value. Because it is one buffer unit, \(q\) below the
minimum data values, \(s_1 = -q\) and \(s_2 = -r_2*q\).

@@

Delaunay triangulation \citep[@albrecht2024]{lee1980} is used to connect
neighboring centroids. The edges are needed to preserve neighborhood
information when the model is lifted into \pD{}.

>>>>

Although there are several implementations of hexagon binning
\citep{carr1987}, and a published paper \citep{dan2023}, surprisingly,
none has sufficient detail or components that produce everything needed
for this project. So we described the process used here.
Figure~\ref{fig-hex-param} illustrates the notation used.

@@

To ensure that the grid covers the range of data values a buffer
parameter (\(q\)) is set as a proportion of the range. By default,
\(q=0.1\). The buffer should be extending a full hexagon width (\(a_1\))
and height (\(a_2\)) beyond the data, in all directions. The lower left
position where the grid starts is defined as \((s_1, s_2)\), and
corresponds to the centroid of the lowest left hexagon,
\(C_{1}^{(2)} = (c_{11}, c_{12})\). This must be smaller than the
minimum data value. Because it is one buffer unit, \(q\) below the
minimum data values, \(s_1 = -q\) and \(s_2 = -qr_2\).

@@

Delaunay triangulation \citep{lee1980, alb2024} is used to connect
neighboring centroids. The edges are needed to preserve neighborhood
information when the model is lifted into \pD{}.
